---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ed0 [![CRAN status](https://www.r-pkg.org/badges/version/ed0)](https://cran.r-project.org/package=ed0) [![License](https://eddelbuettel.github.io/badges/GPL2+.svg)](http://www.gnu.org/licenses/gpl-2.0.html) [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/PMassicotte/ed0?branch=master&svg=true)](https://ci.appveyor.com/project/PMassicotte/ed0) [![Travis build status](https://travis-ci.org/PMassicotte/ed0.svg?branch=master)](https://travis-ci.org/PMassicotte/ed0)

The goal of ed0 is to ...

## Installation

```{r}
# The development version from GitHub:
# install.packages("devtools")
devtools::install_github("pmassicotte/ed0")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE}
library(tidyverse)
library(ed0)

df <- tibble(
  wavelength = seq(290, 700, by = 5),
  ed0 = ed0(100, 12, 67.47973, -63.78953, 3, 330, 1, 0.05)
)

df

df %>% 
  ggplot(aes(x = wavelength, y = ed0)) +
  geom_point() +
  theme_bw()
  

```

## SBDART

The `ed0` package use a look up table (LUT) created from simulations conducted using SBDART (link). SBARDT is a radiative transfert model...

The LUT and the original Fortran code to interpolate the values inside the LUT have been produced by Dr. Simon Bélanger.

## Code of conduct

Please note that the ['ed0' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
